Predicting Infection Outbreak Dynamics in Toronto Healthcare Institutions: A Bayesian Approach

### 2024-12-15 paper/paper.qmd
Update paper.qmd

# Visualisations with the model
logistic_model |> posterior_summary()
```{r}

@@

# Plot with sufficient colors
plot(predicted) +
  scale_color_manual(values = scales::hue_pal()(20)) +  # Generate a palette with at least 20 colors
  labs(
    title = "Predicted Probabilities by Outbreak Setting and Causative Agent",
    x = "Outbreak Setting",
    y = "Predicted Probability",
    color = "Causative Agent"
  ) +
  theme_minimal()
```{r}

>>>>

# Visualisations with the model
logistic_model |> posterior_summary()
```

@@

# Plot with sufficient colors
plot(predicted) +
  scale_color_manual(values = scales::hue_pal()(20)) +  # Generate a palette with at least 20 colors
  labs(
    title = "Predicted Probabilities by Outbreak Setting and Causative Agent",
    x = "Outbreak Setting",
    y = "Predicted Probability",
    color = "Causative Agent"
  ) +
  theme_minimal()
```
